Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-16 paper/paper.tex

\subsection{Partially Observable Markov Decision Processes}
We propose that the brain in general and the DMN in particular 
are a natural system governed by the laws of
physics and can be locally described by Markov processes at a sufficiently coarse scale.
Indeed, as noted in \cite{tegmark2016improved},
any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
step is sufficiently short.
% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state but also on some finite
number of past states.
Rational probabilistic planning can be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include elements of the past.

>>>>

\subsection{Partially Observable Markov Decision Processes}
We propose that the brain in general and the DMN in particular
are a physical system governed by the laws of
physics and can be locally described by Markov processes at a sufficiently coarse scale.
Indeed, as noted in \cite{tegmark2016improved},
any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
step is sufficiently short.
% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state but also on some finite
number of past states.
Rational probabilistic planning can be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include elements of the past.
